this is for the result part of the draft

### 2017-03-24 analysis/draft.Rmd
Files commited by wflow_commit.

This data set is summary statistics (Z-score) from eQTL analysis.

@@

The Breast cancer data is from West et al. (2007). There are 251 samples and 226 genes in this data set. For those algorithm we choose, we set the rank equal to 50 which is close the the rank of the estimation from the NSFA results. After some try of FLASH, we find that the rank picked by FLASH is also around 40-50. Following the pre-processing procedure from NSFA, we also use the centered data.

@@

We apply FLASH on the matrix of summary statistics which are Z-scores.

"We analysed the 16,069 genes for which univariate effect estimates were available for all 44 tissues we considered; the filtering criteria used ensure that these genes show at least some indication of expression in all 44 tissues."

As input to mash we use a matrix of eQTL effect estimates ˆbjr, and
corresponding standard errors ˆsij , where the rows j index different SNP-gene
pairs and the columns r index tissues (or cell types). We used the effect
estimates and standard errors for candidate local (“cis”) eQTLs for each gene,
distributed by the GTEx project (v6 release). These were obtained by
(univariate) single-SNP analyses in each tissue by applying MatrixEQTL [20] on
expression levels that have been rank-transformed to the corresponding
quantiles of a standard normal distribution. Thus the effect size estimates are in
units of standard deviations on this transformed scale. Because, like most eQTL
analyses, these estimates were obtained by single-SNP analysis, the estimated
effects for each SNP actually reflect the effects of both the SNP itself and other
SNPs in LD with it (see Supplementary Text for discussion). We analysed the
16,069 genes for which univariate effect estimates were available for all 44 tissues
we considered; the filtering criteria used ensure that these genes show at least
some indication of expression in all 44 tissues.

>>>>

This data set is summary statistics (Z-score) from eQTL analysis. We apply FLASH on the matrix of summary statistics which are Z-scores with , where the rows index different SNP-gene pairs and the columns index tissues (or cell types). We used the Z-scores for candidate local (“cis”) eQTLs for each gene, distributed by the GTEx project (v6 release).

@@

The Breast cancer data is from West et al. (2007). There are 251 samples and 226 genes in this data set. For those algorithm we choose, we set the rank equal to 50 which is close the the rank of the estimation from the NSFA results. After some try of FLASH, we find that the rank picked by FLASH is also around 40-50. Following the pre-processing procedure from NSFA, we also use the centered data. Since this input data set is Z-scores data, we didn't use any pre-processing procedure.

@@

We apply FLASH on the matrix of summary statistics which are Z-scores. "We analysed the 16,069 genes for which univariate effect estimates were available for all 44 tissues we considered; the filtering criteria used ensure that these genes show at least some indication of expression in all 44 tissues."
